### 2022-03-24 paper/output/document/thesis_5_discussion.tex
submit

This work is an early proof-of-concept. It demonstrates the potential of top-down, logic programming 

@@

could be used in practice, but this project demonstrates that these questions are within closer reach

@@

%:%766=637%:%
%:%767=638%:%
%:%768=639%:%
%:%769=640%:%
%:%770=641%:%
%:%771=642%:%
%:%774=643%:%
%:%775=644%:%
%:%776=645%:%
%:%777=646%:%
%:%778=647%:%
%:%779=648%:%

@@

%:%798=662%:%
%:%810=664%:%
%:%811=665%:%
%:%812=666%:%
%:%813=667%:%
%:%814=668%:%
%:%815=669%:%

@@

%:%870=717%:%
%:%882=719%:%
%:%883=720%:%
%:%884=721%:%
%:%885=722%:%
%:%886=723%:%
%:%887=724%:%

@@

>>>>

This work is an early proof-of-concept. It demonstrates the potential of top-down

@@

could be used in practice, but this project demonstrates that answers to these questions are within closer reach

@@

%:%764=636%:%
%:%765=637%:%
%:%766=638%:%
%:%767=639%:%
%:%768=640%:%
%:%769=641%:%
%:%772=643%:%
%:%773=644%:%
%:%774=645%:%
%:%775=646%:%
%:%776=647%:%
%:%777=648%:%

@@

%:%790=659%:%
%:%791=660%:%
%:%792=661%:%
%:%793=662%:%
%:%794=663%:%
%:%795=664%:%
%:%804=668%:%

@@

%:%862=716%:%
%:%863=717%:%
%:%864=718%:%
%:%865=719%:%
%:%866=720%:%
%:%867=721%:%
%:%876=723%:%

@@

%:%921=758%:%
%:%922=759%:%
%:%923=760%:%
%:%924=761%:%
%:%925=762%:%
%:%926=763%:%
